---
title: "p8105_hw6_hm2947"
author: "Matthew Ma"
date: "2022-12-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_libraries, message=FALSE}
library(tidyverse)
library(modelr)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 


### Problem 2

## Data cleaning and tidying

```{r}
homicide_df = read.csv("./data/homicide-data.csv") %>%
  janitor::clean_names()
```

```{r}
homi_tidy = homicide_df %>% 
  mutate(city_state = str_c(city, "," , state)) %>% 
  mutate(status = ifelse(disposition == "Closed by arrest", 1, 0), 
         victim_age = as.numeric(victim_age)) %>% 
  filter(!city_state %in% c("Dallas,TX", "Phoenix,AZ", "Kansas City,MO", "Tulsa,AL")) %>% 
  filter(victim_race %in% c("White", "Black"))
```

## Baltimore regression model

```{r}
baltimore = 
  homi_tidy %>% 
  filter(city_state == "Baltimore,MD")

baltimore_fit = 
  baltimore %>%
  glm(status ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(odds_ratio = exp(estimate),
         lower_bound = exp(estimate - 1.96*std.error),
         upper_bound = exp(estimate + 1.96*std.error)) %>%
    filter(term == "victim_sexMale") %>%
  select(term, odds_ratio, lower_bound, upper_bound )

  baltimore_fit %>% 
    knitr::kable(digits = 3)
```



