---
title: "p8105_hw6_hm2947"
author: "Matthew Ma"
date: "2022-12-03"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_libraries, message=FALSE}
library(tidyverse)
library(modelr)
library(purrr)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 


### Problem 2

## Data cleaning and tidying

```{r}
homicide_df = read.csv("./data/homicide-data.csv") %>%
  janitor::clean_names()
```

```{r}
homi_tidy = homicide_df %>% 
  mutate(city_state = str_c(city, "," , state)) %>% 
  mutate(status = ifelse(disposition == "Closed by arrest", 1, 0), 
         victim_age = as.numeric(victim_age)) %>% 
  filter(!city_state %in% c("Dallas,TX", "Phoenix,AZ", "Kansas City,MO", "Tulsa,AL")) %>% 
  filter(victim_race %in% c("White", "Black"))
```

## Baltimore regression model

```{r}
baltimore = 
  homi_tidy %>% 
  filter(city_state == "Baltimore,MD")

baltimore_fit = 
  baltimore %>%
  glm(status ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(odds_ratio = exp(estimate),
         lower_bound = exp(estimate - 1.96*std.error),
         upper_bound = exp(estimate + 1.96*std.error)) %>%
    filter(term == "victim_sexMale") %>%
  select(term, odds_ratio, lower_bound, upper_bound )

  baltimore_fit %>% 
    knitr::kable(digits = 3)
```

## glm for all cities in the dataset

```{r}

city_all = 
  homi_tidy %>% 
  nest(data = -city_state) %>% 
  mutate(models = map(.x = data, ~ glm(status ~ victim_age + victim_race + victim_sex, data = .x, family = "binomial")),
    results = map(models, broom::tidy)
    ) %>% 
  unnest(results) %>% 
  mutate(odds_ratio = exp(estimate),
         lower_bound = exp(estimate - 1.96*std.error),
         upper_bound = exp(estimate + 1.96*std.error)) %>%
    filter(term == "victim_sexMale") %>%
  select(city_state, odds_ratio, lower_bound, upper_bound )
  
city_all %>% 
  knitr::kable(digit = 3)
```

## Plotting the estimated ORs and CIs for each city

```{r}

city_all %>% 
  mutate(city_state = fct_reorder(city_state, odds_ratio)) %>% 
  ggplot(aes(x = city_state, y = odds_ratio)) +
  geom_point() +
  geom_errorbar(mapping = aes(ymin = lower_bound, ymax = upper_bound))  +
  labs( x = "City, State",  y = "Odds Ratio", title = "Estimated Odds Ratio and Confidence Intervals of Solving Homicides Comparing Male and Female Victims for Each City ") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

For the majority of the cities investigated, the odds ratio of solving homicides between male and female victims lies in between 0 and 1. Out of the 50 cities, there are only 4 cities' odds ratio has gone beyond 1 which are `Nashville,TN`, `Fresno,CA`, `Stockton,CA`, and `Albuquerque,NM`. The last three cities mentioned have much larger odds ratio than others also with much larger confidence intervals. Larger standard errors could also be inferred.

### Problem 3

## Load and Clean

```{r}

bw_df = read_csv("./data/birthweight.csv")

bw_tidy = 
  bw_df %>%
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace), 
         malform = as.factor(malform), 
         mrace = as.factor(mrace)
         )
sum(!complete.cases(bw_tidy))
# there is no missing values
```

## Proposing a regression model for birthweight

First I conduct a stepwise method for variable selection.

```{r}
model_0 <- lm(bwt ~.,
               data =bw_tidy)
step(model_0, direction = "both", trace  = FALSE)
summary(model_0)

```

According to the summary of the stepwise model selections we could choose `babysex`, `bhead`, `blength`, `delwt`, `fincome`, `gaweeks`, `mheight`, `mrace`, `parity`, `ppwt`, `smoken` as our variables. 

## Show a plot of model residuals against fitted values

```{r}

resi_vs_fit =
  bw_tidy %>% 
  add_predictions(model_0) %>% 
  add_residuals(model_0) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_smooth(formula = 'y ~ x',method = "lm", se = FALSE) +
  labs(title = "Fitted Values vs. Residuals",
       x = "Fitted Values", 
       y = "Residuals",) +
  theme(plot.title = element_text(hjust = 0.5))

resi_vs_fit
```
 From the plot we could observe a cluster of residual points around 0 that fit mostly between 2000-4000. There are some outlying values that are below 1000 fitted value.
 
## Compare with two other models.

```{r}

model_1 = lm(bwt ~ blength + gaweeks, data = bw_tidy)

model_2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex,
               data = bw_tidy)
```

## Cross-validation

```{r}

cv_df = 
  crossv_mc(bw_tidy, 100) %>% 
  mutate(train = map(train, as_tibble),
    test = map(test, as_tibble))%>% 
  mutate(
    model_1  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_2  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x)),
    model_0  = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x ))) %>% 
  mutate(
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2    = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_model_0 = map2_dbl(model_0, test, ~rmse(model = .x, data = .y)))
  

cv_df %>% 
  select(starts_with("rmse")) %>%
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>%
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(title = "Comparison of the Cross-Validated Prediction Error", 
       x = "Models", 
       y = "Root Mean Square Error (RMSE)") 

  
```

According to the violin plot, model_0 which is my model has the lowest rmse score which indicates the best model among the three models compared to the other two.

